### 2022-02-23 sections/strategy_Htautau.tex
updates with EB comments

The $tt(qH)$ and $tH$ signal being probed are characterised by the presence of $\tau$-leptons from the decay of 
the Higgs boson, where the remaining top quark decays into $Wb$. There is an additional $q$-jet from the FCNC $t\to qH$ decay in the top pair production. 
%at least  four (three) jets in the decay (production) mode, only one of which originates from a $b$-quark.
If the $W$ boson or one of the $\tau$-leptons decays leptonically, an isolated electron or muon, together with significant $\met$ is also expected.
In a significant fraction of the events, the lowest $\pt$ jet from the hadronic $W$ boson decay fails the minimum $\pt$ requirement of $25~\gev$,
resulting in only three reconstructed jets where the production mode is dominant. 
%some signal events mixed with production mode having only three reconstructed jets.
In order to optimise the sensitivity of the search, the selected events are categorised into seven SRs based on the number of light leptons,
$\had$ candidates, and on the number of light flavored jets:
$t_l\hadhad$, $t_l\had$-1j, $t_l\had$-2j, $t_h\lephad$-2j, $t_h\lephad$-3j, $t_h\hadhad$-2j, and $t_h\hadhad$-3j, as shown in Table~\ref{tab:srcr}.

%   \begin{table}
%   \centering
%   \caption{Overview of the signal regions and the control regions used for fake tau scale factor derivation in leptonic channels.}
%   \label{tab:srcr}
%   \begin{tabular}[h]{c|c|c|c|c|c|c}
%   \hline \hline
%   \multicolumn{2}{c|}{Regions} & $b$-jet & light flavor jets        & lepton & hadronic taus & charge\\ \hline
%   \multirow{7}{*}{SR}&$t_l\thadhad$     & 1     & any                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
%   &$t_l\tauhad$-1j  & 1     & 1                                   & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
%   &$t_l\tauhad$-2j  & 1     & 2                                        & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
%   &$t_h\tlhad$-2j   & 1     & 2                           & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
%   &$t_h\tlhad$-3j   & 1     & $\ge3$                      & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
%   &$t_h\thadhad$-2j & 1     & 2                            & 0      & 2             & $\thadhad$ OS\\ \cline{2-7}
%   &$t_h\thadhad$-3j & 1     & $\ge3$                       & 0      & 2             & $\thadhad$ OS\\ \hline
%   \multirow{6}{*}{CRtt}&$t_lt_l1b\tauhad$ & 1     & any                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
%   &$t_lt_l2b\tauhad$      & 2     & any                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
%   &$t_lt_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
%   &$t_lt_h2b\tauhad$-2jOS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ OS\\ \cline{2-7}
%   &$t_lt_h2b\tauhad$-3jSS & 2     & $\ge3$                        & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
%   &$t_lt_h2b\tauhad$-3jOS & 2     & $\ge3$                & 1      & 1             & $t_l\tauhad$ OS\\ \hline
%   \end{tabular}
%   \end{table}

\begin{table}
\centering
\caption{Overview of the signal regions (SR) and the $t\bar{t}$ control regions (CRtt) used for fake tau scale factor derivation in leptonic channels. Leptons are required to have either same-sign (SS) or opposite-sign (OS) charges in each region.}
\label{tab:srcr}
\begin{tabular}[h]{c|c|c|c|c|c|c}
\hline \hline
\multicolumn{2}{c|}{Regions} & $b$-jet & light flavor jets        & lepton & hadronic taus & charge\\ \hline
\multirow{7}{*}{SR}&$t_l\thadhad$     & 1     & $\ge0$                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
&$t_l\tauhad$-1j  & 1     & 1                                   & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
&$t_l\tauhad$-2j  & 1     & 2                                        & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
&$t_h\tlhad$-2j   & 1     & 2                           & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
&$t_h\tlhad$-3j   & 1     & $\ge3$                      & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
&$t_h\thadhad$-2j & 1     & 2                            & 0      & 2             & $\thadhad$ OS\\ \cline{2-7}
&$t_h\thadhad$-3j & 1     & $\ge3$                       & 0      & 2             & $\thadhad$ OS\\ \hline
\multirow{6}{*}{CRtt}&$t_lt_l1b\tauhad$ & 1     & $\ge0$                            & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
&$t_lt_l2b\tauhad$      & 2     & $\ge0$                            & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
&$t_lt_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
&$t_lt_h2b\tauhad$-2jOS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ OS\\ \cline{2-7}
&$t_lt_h2b\tauhad$-3jSS & 2     & $\ge3$                        & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
&$t_lt_h2b\tauhad$-3jOS & 2     & $\ge3$                & 1      & 1             & $t_l\tauhad$ OS\\ \hline
\end{tabular}
\end{table}

@@

For the $t_ht(qH)$ events, the jet from $t\to qH$, denoted as the FCNC jet ($q$-jet), should be a hard narrow jet from the
decay chain $t\to qH\to q\tau\tau$, with taus reconstructed as $\lephad$ or $\hadhad$.
There should be at least four jets among which the one with the smaller angular distance to the visible decay of the di-tau,
is considered as the $q$-jet since the FCNC top decay products are likely boosted closer together than other jets. 
If there are more than two jets besides the $q$- and $b$-jet, the jets from $W$ boson decay are chosen from the combination
with the invariant mass closest to the $W$ boson mass. There is the chance that one of the jets fails the $\pt$ requirement and is not reconstructed.
This kind of events will fall into $t_hH$.
%while the FCNC top resonance is
%still reconstructable that the missing jet is likely from the decay of $W$ boson.
%given the big chance that the jet which is missing is from $W$ decay.
In the $t_hH$ events, there are three jets coming from top hadronic decay including the $b$-jet and two opposite-sign $\had$ from the Higgs boson decay, where
both $t_h$ and $H$ can be reconstructed.  
%. So a Higgs resonance formed by the taus and a top resonance formed by
%the jets are expected.

@@

For the  $t_lt(qH)$ and $t_lH$ events where the $W$ boson from $t\to W b$ decay decays leptonically,
%has a large momentum and the flying direction is unknown.
the kinematic fit is no longer feasible due to extra neutrino from $W\rightarrow \ell\nu$ decay. The kinematic variables are calculated using the visible
objects only. After the event reconstruction, a number of variables are used to discriminate the signal from the background using a multivariate analysis described
in Section~\ref{sec:tmva}.

@@

%In the  $t_lt(qH)$ and $t_lH$ signal, the additional $q$ jet in the decay mode can still be found, but since the $W$ boson decays leptonically, there is a neutrino with large momentum and the flying direction is unknown. The kinematics fit is no longer feasible in the $t_l\hadhad$ channel. The variables calculated from the visible objects are directly used in the multivariate analysis. However, the kinematics fit is still performed for the $t_l\had$ channels where the lepton and $\had$ are treated as di-tau candidate.

@@

   & $t_{l}\tauhad$-1j                                  &  $t_{h}\tlhad$-2j   &  $t_{l}\tauhad$-2j & $t_{h}\tlhad$-3j & $t_l2\tauhad$     & $t_h2\tauhad$-2j & $t_h2\tauhad$-3j       \\\midrule

@@

 $m_{\text{W}}$                                      &   &             &           & $9$      &       & $6$      & $7$\\

@@

 $m^{\text{T}}_{\text{W}}$                           & $11$      &             &  $8$              &  & $13$          &  &         \\
 $m_{\tau,\tau}$                                     &   &  $2$                &           & $3$      &       & $1$      & $1$          \\
 $m_{\text{t},\text{SM}}$                            &   &  $1$                &           & $2$      &       & $3$      & $4$          \\

@@

 $m_{\text{t},\text{FCNC}}$                          &   &             &           &  &       & $10$     & $6$\\
 $m_{\text{t},\text{SM},\text{vis}}$                 & $3$       &             &  $5$              &  & $4$           &  &         \\
 ${\pt}_{\tauhadvis}$                                 & $1$       &  $4$                &  $1$              & $1$      & $5$           & $11$   & $10$           \\

@@

 $m_{\tau\tau,\text{vis}}$                           & $10$      &  $14$               &  $11$             & $6$      & $1$           & $2$    & $2$          \\
 $E_{\text{vis}~\tau1}/E_{\tau1}$                  &   &  $10$               &           & $12$     &       & $8$    & $8$          \\
 $E_{\text{vis}~\tau2}/E_{\tau2}$                  &   &  $7$                &           & $4$      &       & $9$    & $11$         \\
 $P_{\text{T,\tauhadvis}} $                          &   &             &           &  & $9$           &  &         \\
 $m_{\text{t},\text{FCNC},\text{vis}}$               &   &             &           &  & $3$           &  &        \\

@@

 \text{min}($m_{\tau\tau j/g}$)             & $9$       &             &  $3$              &  & $14$          &  &         \\

@@

Boosted decision trees (BDT) implemented in the TMVA framework~\cite{Hocker:2007ht} are used in each SR to improve the separation between signal and background. 
%The separate training exploits differences in event kinematics across SRs.  
%draft 1 version
In the training, all signal events from $tt(qH)$ and $tH$ are merged together for $tuH$ and $tcH$. All background sources from SM processes
(including both real and fake $\had$ contributions) are also used in the training.

@@

\item ${\pt}_{\tauhadvis} $ is the transverse momentum of the leading tau candidate.
\item ${\pt}_{\text{sub}-\tau}$ is the transverse momentum of the sub-leading tau candidate.

@@

\item $m_{t,\text{SM}}$ is the invariant mass of the $b$-jet and the two jets from the $W$ decay, and reflects the top mass in the decay $t\to Wb \to j_1j_2b$. This variable is only defined for the 4-jet $t_hH$ and $t_ht(qH)$ events.
\item $m^{T}_{\text{W}}$ is the transverse mass calculated from the lepton and $\met$ in the leptonic channels, defined as

@@

m^{T}_{\text{W}} = \sqrt{2 {\pt}_{\ell} E_{\text{T}}^{\text{miss}} \left(1-\cos\Delta\phi_{\ell,\text{miss}} \right)},  

@@

\item $m_{\tau,\tau}$ is the fitted invariant mass of the tau candidates and reconstructed neutrinos in the $t_hH$, $t_ht(qH)$ channels. 
\item $m_{\text{W}}$ is the reconstructed invariant mass of two light-jets from the $W$ decay with the mass closet to the $W$ mass.
\item $m_{\text{t},\text{FCNC}}$ is the fitted invariant mass of the FCNC-decaying top quark reconstructed from di-tau candidates, $q$-jet and reconstructed neutrinos.
\item $m_{\tau\tau,\text{vis}}$ is the visible invariant mass of the di-tau candidates. %or the lepton and $\had$ candidate when there is only one $\had$.
\item ${\pt}_{\tau\tau,\text{vis}}$ is the visible $\pT$ of the di-tau candidates.
\item $m_{\text{t},\text{FCNC},\text{vis}}$ is the reconstructed visible mass of the FCNC-decaying top quark.
\item $m_{\text{t},\text{SM},\text{vis}}$ is the invariant mass of the lepton and the $b$-jet, which reflects the visible top quark mass.
\item \text{min}($m_{\tau\tau j/q}$) is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative to variable $m_{\text{t},\text{FCNC},\text{vis}}$.
\item \text{min}($m_{jj}$) is the invariant mass of two light-flavor jets, minimized by choosing different jets, reflects the invariant mass of the W candidate.

@@

\item $E_{\text{vis}~\tau\text{i}}/E_{\tau\text{i}},\text{i}=1,2$ is the momentum fraction carried by the visible decay products from the tau mother. It is based on the best-fit 4-momentum of the neutrino(s) according to the event reconstruction algorithm in this section. For the $\tauhad$ decay mode, the visible decay products carry most of the tau energy since there is only a single neutrino in the final state.% which is evident in the excess around 1 in Figure \ref{fig:x12_fit}. 

@@

\item $\Delta\phi(\tau\tau,\met)$ is the azimuthal angle between the $\met$ and di-tau $\pT$.

@@

A comparison between data and the predicted background for the leading $\had$ $\pt$ distribution in the SRs 
%some of these variables in three main decay final states($t_l\hadhad$, $t_h\hadhad$, and $t_h\lephad$)
is shown in Figure~\ref{fig:taupt_prefit}.
%each of the SRs considered is shown in Figures~\ref{fig:mva_input_hadhad} -~\ref{fig:mva_input_lhadhad}.
%The comparison between the data and predicted background after preselection for the distributions of two of the most 
%discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit'').
%The expected signals are also shown after scaled up for the shape comparison of the distributions.
%by a large factor normalized to the total number of events in the predicted
%background for the shape comparison.   
%corresponding to $\BR(t\to Hq)=0.2\%$ is also shown.
The last bin of each plot contains the overflow entries.
The bottom panel displays the ratio of data to the background (``Bkg'') prediction as discussed in section~\ref{sec:background_model}.
The hashed area represents the total uncertainty of the background.
A good description of the data by the background model is observed in all cases.
The final observable used to extract the signal contribution is the BDT distribution in each SR corresponding to either $tuH$ or $tcH$ signal.

>>>>

The $tt(qH)$ and $tH$ signal being probed are characterised by the presence of $\tau$-leptons from the decay of 
the Higgs boson, where the remaining top quark decays into $Wb$. There is an additional $q$-jet from the FCNC $t\to qH$ decay in the top pair production. 
%at least  four (three) jets in the decay (production) mode, only one of which originates from a $b$-quark.
If the $W$ boson or one of the $\tau$-leptons decays leptonically, an isolated electron or muon, together with significant $\met$ is also expected.
In a significant fraction of the events, the lowest $\pt$ jet from the hadronic $W$ boson decay fails the minimum $\pt$ requirement of $25~\gev$,
resulting in only three reconstructed jets where the production mode is dominant. 
%some signal events mixed with production mode having only three reconstructed jets.
In order to optimise the sensitivity of the search, the selected events are categorised into seven SRs based on the number of light leptons,
$\had$ candidates, and on the number of light flavored jets:
$t_{\ell}\hadhad$, $t_{\ell}\had$-1j, $t_{\ell}\had$-2j, $t_h\lephad$-2j, $t_h\lephad$-3j, $t_h\hadhad$-2j, and $t_h\hadhad$-3j, as shown in Table~\ref{tab:srcr}.

%   \begin{table}
%   \centering
%   \caption{Overview of the signal regions and the control regions used for fake tau scale factor derivation in leptonic channels.}
%   \label{tab:srcr}
%   \begin{tabular}[h]{c|c|c|c|c|c|c}
%   \hline \hline
%   \multicolumn{2}{c|}{Regions} & $b$-jet & light flavor jets        & lepton & hadronic taus & charge\\ \hline
%   \multirow{7}{*}{SR}&$t_{\ell}\thadhad$     & 1     & any                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
%   &$t_{\ell}\tauhad$-1j  & 1     & 1                                   & 1      & 1                     & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
%   &$t_{\ell}\tauhad$-2j  & 1     & 2                                        & 1      & 1                     & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
%   &$t_h\tlhad$-2j   & 1     & 2                           & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
%   &$t_h\tlhad$-3j   & 1     & $\ge3$                      & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
%   &$t_h\thadhad$-2j & 1     & 2                            & 0      & 2             & $\thadhad$ OS\\ \cline{2-7}
%   &$t_h\thadhad$-3j & 1     & $\ge3$                       & 0      & 2             & $\thadhad$ OS\\ \hline
%   \multirow{6}{*}{CRtt}&$t_{\ell}t_{\ell}1b\tauhad$ & 1     & any                           & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
%   &$t_{\ell}t_{\ell}2b\tauhad$      & 2     & any                           & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
%   &$t_{\ell}t_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
%   &$t_{\ell}t_h2b\tauhad$-2jOS & 2     & 2                             & 1      & 1             & $t_{\ell}\tauhad$ OS\\ \cline{2-7}
%   &$t_{\ell}t_h2b\tauhad$-3jSS & 2     & $\ge3$                        & 1      & 1             & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
%   &$t_{\ell}t_h2b\tauhad$-3jOS & 2     & $\ge3$                & 1      & 1             & $t_{\ell}\tauhad$ OS\\ \hline
%   \end{tabular}
%   \end{table}

\begin{table}
\centering
\caption{Overview of the signal regions (SR) and the $t\bar{t}$ control regions (CRtt) used for fake tau scale factor derivation in leptonic channels. Leptons are required to have either same-sign (SS) or opposite-sign (OS) charges in each region.}
\label{tab:srcr}
\begin{tabular}[h]{c|c|c|c|c|c|c}
\hline \hline
\multicolumn{2}{c|}{Regions} & $b$-jet & light flavor jets        & lepton & hadronic taus & charge\\ \hline
\multirow{7}{*}{SR}&$t_{\ell}\thadhad$     & 1     & $\ge0$                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
&$t_{\ell}\tauhad$-1j  & 1     & 1                                   & 1      & 1                     & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
&$t_{\ell}\tauhad$-2j  & 1     & 2                                        & 1      & 1                     & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
&$t_h\tlhad$-2j   & 1     & 2                           & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
&$t_h\tlhad$-3j   & 1     & $\ge3$                      & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
&$t_h\thadhad$-2j & 1     & 2                            & 0      & 2             & $\thadhad$ OS\\ \cline{2-7}
&$t_h\thadhad$-3j & 1     & $\ge3$                       & 0      & 2             & $\thadhad$ OS\\ \hline
\multirow{6}{*}{CRtt}&$t_{\ell}t_{\ell}1b\tauhad$ & 1     & $\ge0$                            & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
&$t_{\ell}t_{\ell}2b\tauhad$      & 2     & $\ge0$                            & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
&$t_{\ell}t_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
&$t_{\ell}t_h2b\tauhad$-2jOS & 2     & 2                             & 1      & 1             & $t_{\ell}\tauhad$ OS\\ \cline{2-7}
&$t_{\ell}t_h2b\tauhad$-3jSS & 2     & $\ge3$                        & 1      & 1             & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
&$t_{\ell}t_h2b\tauhad$-3jOS & 2     & $\ge3$                & 1      & 1             & $t_{\ell}\tauhad$ OS\\ \hline
\end{tabular}
\end{table}

@@

For the $t_ht(qH)$ events, the jet from $t\to qH$, denoted as the FCNC jet ($q$-jet), should be a hard narrow jet from the
decay chain $t\to qH\to q\tau\tau$, with taus reconstructed as $\lephad$ or $\hadhad$.
There should be at least four jets among which the one with the smaller angular distance to the visible decay of the di-tau,
is considered as the $q$-jet since the FCNC top decay products are likely boosted closer together than other jets. 
If there are more than two jets besides the $q$- and $b$-jet, the jets from $W$ boson decay are chosen from the combination
with the invariant mass closest to the $W$ boson mass. There is the chance that one of the jets fails the $\pt$ requirement and is not reconstructed.
This kind of events will fall into $t_hH$ final state.
%while the FCNC top resonance is
%still reconstructable that the missing jet is likely from the decay of $W$ boson.
%given the big chance that the jet which is missing is from $W$ decay.
There are three jets coming from top hadronic decay including the $b$-jet and a pair of opposite-sign taus from the Higgs boson decay, where
both $t_h$ and $H$ can be reconstructed.  
%. So a Higgs resonance formed by the taus and a top resonance formed by
%the jets are expected.

@@

For the  $t_{\ell}t(qH)$ and $t_{\ell}H$ events where $W$ boson from $t\to W b$ decay decays leptonically,
%has a large momentum and the flying direction is unknown.
the kinematic fit is no longer feasible due to extra neutrino from $W\rightarrow \ell\nu$ decay. The kinematic variables are calculated using the visible
objects only. After the event reconstruction, a number of variables are used to discriminate the signal from the background using a multivariate analysis described
in Section~\ref{sec:tmva}.

@@

%In the  $t_{\ell}t(qH)$ and $t_{\ell}H$ signal, the additional $q$ jet in the decay mode can still be found, but since the $W$ boson decays leptonically, there is a neutrino with large momentum and the flying direction is unknown. The kinematics fit is no longer feasible in the $t_{\ell}\hadhad$ channel. The variables calculated from the visible objects are directly used in the multivariate analysis. However, the kinematics fit is still performed for the $t_{\ell}\had$ channels where the lepton and $\had$ are treated as di-tau candidate.

@@

   & $t_{l}\tauhad$-1j                                  &  $t_{h}\tlhad$-2j   &  $t_{l}\tauhad$-2j & $t_{h}\tlhad$-3j & $t_{\ell}2\tauhad$     & $t_h2\tauhad$-2j & $t_h2\tauhad$-3j       \\\midrule

@@

 $m_{\text{jj}}$                                      &   &             &           & $9$      &       & $6$      & $7$\\

@@

 $m^{W}_{\text{T}}$                           & $11$      &             &  $8$              &  & $13$          &  &         \\
 $m_{\tau\tau,\text{fit}}$                                     &   &  $2$                &           & $3$      &       & $1$      & $1$          \\
 $m_{\text{bjj},\text{fit}}$                            &   &  $1$                &           & $2$      &       & $3$      & $4$          \\

@@

 $m_{\tau\tau\text{q},\text{fit}}$                          &   &             &           &  &       & $10$     & $6$\\
 $m_{\text{bjj}}$                 & $3$       &             &  $5$              &  & $4$           &  &         \\
 ${\pt}_{\tau1}$                                 & $1$       &  $4$                &  $1$              & $1$      & $5$           & $11$   & $10$           \\

@@

 $m_{\tau\tau}$                           & $10$      &  $14$               &  $11$             & $6$      & $1$           & $2$    & $2$          \\
 $E_{\tau1}/E_{\tau1,\text{fit}}$                  &   &  $10$               &           & $12$     &       & $8$    & $8$          \\
 $E_{\tau2}/E_{\tau2,\text{fit}}$                  &   &  $7$                &           & $4$      &       & $9$    & $11$         \\
 ${\pt}_{\tautau} $                          &   &             &           &  & $9$           &  &         \\
 $m_{\tau\tau\text{q}}$               &   &             &           &  & $3$           &  &        \\

@@

 \text{min}($m_{\tau\tau \text{j}}$)             & $9$       &             &  $3$              &  & $14$          &  &         \\

@@

Boosted decision trees (BDT) implemented in the TMVA framework~\cite{Hocker:2007ht} are used in each SR to improve the separation between signal and background. 
%The separate training exploits differences in event kinematics across SRs.  
%draft 1 version
In the training, all signal events from $tt(qH)$ and $tH$ are merged together for $tuH$ and $tcH$. All background sources from SM processes
(including both real and fake tau contributions) are also used in the training.

@@

\item ${\pt}_{\tau1} $ is the transverse momentum of the leading tau candidate.
\item ${\pt}_{\tau2}$ is the transverse momentum of the sub-leading tau candidate.

@@

\item $m_{\text{bjj},\text{fit}}$ is the fitted invariant mass of the $b$-jet and the two jets from the $W$ decay, and reflects the top mass in the decay $t\to Wb \to j_1j_2b$. This variable is only defined for the 4-jet $t_hH$ and $t_ht(qH)$ events.
\item $m^{W}_{\text{T}}$ is the transverse mass calculated from the lepton and $\met$ in the leptonic channels, defined as

@@

m^{W}_{\text{T}} = \sqrt{2 {\pt}_{\ell} E_{\text{T}}^{\text{miss}} \left(1-\cos\Delta\phi_{\ell,\text{miss}} \right)},  

@@

\item $m_{\tau\tau,\text{fit}}$ is the fitted invariant mass of the tau candidates and reconstructed neutrinos for the $t_hH$ and $t_ht(qH)$ events. 
\item $m_{\text{jj}}$ is the reconstructed invariant mass of two light-jets from the $W$ decay with the mass closet to the $W$ mass.
\item $m_{\tau\tau\text{q},\text{fit}}$ is the fitted invariant mass of the FCNC-decaying top quark reconstructed from di-tau candidates, $q$-jet and reconstructed neutrinos.
\item $m_{\tau\tau}$ is the visible invariant mass of the di-tau system. %or the lepton and $\had$ candidate when there is only one $\had$.
\item ${\pt}_{\tau\tau}$ is the visible $\pT$ of the di-tau system.
\item $m_{\tau\tau,\text{q}}$ is the reconstructed visible mass of the FCNC-decaying top quark.
\item $m_{\text{bjj}}$ is the invariant mass of the lepton and the $b$-jet, which reflects the visible top quark mass.
\item \text{min}($m_{\tau\tau \text{j}}$) is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative to variable $m_{\tautau\text{q}}$.
\item \text{min}($m_{\text{jj}}$) is the invariant mass of two light-flavor jets, minimized by choosing different jets, reflects the invariant mass of the W candidate.

@@

\item $E_{\tau\text{i}}/E_{\tau\text{i},\text{fit}}$, \text{i}=1,2 are the momentum fraction carried by the visible decay products from the leading and subleading tau decays. It is based on the best-fit 4-momentum of the neutrino(s) according to the event reconstruction algorithm in this section. For the $\tauhad$ decay mode, the visible decay products carry most of the tau energy since there is only a single neutrino in the final state.% which is evident in the excess around 1 in Figure \ref{fig:x12_fit}. 

@@

\item $\Delta\phi(\tau\tau,\met)$ is the azimuthal angle between the $\met$ and di-tau system $\pT$.

@@

A comparison between data and the predicted background for the leading tau $\pt$ distribution in the SRs 
%some of these variables in three main decay final states($t_{\ell}\hadhad$, $t_h\hadhad$, and $t_h\lephad$)
is shown in Figure~\ref{fig:taupt_prefit}.
%each of the SRs considered is shown in Figures~\ref{fig:mva_input_hadhad} -~\ref{fig:mva_input_{\ell}hadhad}.
%The comparison between the data and predicted background after preselection for the distributions of two of the most 
%discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit'').
%The expected signals are also shown after scaled up for the shape comparison of the distributions.
%by a large factor normalized to the total number of events in the predicted
%background for the shape comparison.   
%corresponding to $\BR(t\to Hq)=0.2\%$ is also shown.
The last bin of each plot contains the overflow entries.
The bottom panel displays the ratio of data to the background (``Bkg'') prediction as discussed in section~\ref{sec:background_model}.
The hashed area represents the total uncertainty of the background.
A good description of the data by the background model is observed in all cases.
The final observable used to extract the signal contribution is the BDT distribution in each SR corresponding to either $tuH$ or $tcH$ signal.

%Figure~\ref{fig:asimov_prefitbdt} show the postfits to the data of BDT observable in each SRs with all background processes constrained to the SM expectation.
%The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{\FCNCFigures/tex/BDTinput}
\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l2tau1bnj_os.pdf} &
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b1j_ss.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_ss.pdf}\\
(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_os.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b3j_os.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b2jos_vetobtagwp70_highmet.pdf}\\
(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b3jos_vetobtagwp70_highmet.pdf}&\\
(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tuH$ signals in: $t_{\ell}\thadhad$ (a1),  $t_{\ell}\tauhad$-1j (a2),  $t_{\ell}\tauhad$-2j (a3), $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (b3), and $t_h\thadhad$-3j (c1) before the fit to data ('Pre-Fit'). The uncertainty band includes both the statistical and systematic uncertainties in the background prediction. Overflow bins are included respectively in the last bin. Others (Rare) includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) 
channels. 
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the ratios of the data to the background prediction.}
\label{fig:taupt_prefit}
\end{figure}

% %\input{\FCNCFigures/tex/BDT}
% \begin{figure}[H]
% \centering
% \begin{tabular}{@{}ccc@{}}
% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/BDTG_test.pdf} &
% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/BDTG_test.pdf}&
% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/BDTG_test.pdf}\\
% (a1) BDT discriminant in $t_{\ell}\thadhad$ & (a2) BDT discriminant in  $t_{\ell}\tauhad$-1j& (a3) BDT discriminant in $t_{\ell}\tauhad$-2j\\
% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_os_vetobtagwp70_highmet/BDTG_test.pdf} &
% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b3j_os_vetobtagwp70_highmet/BDTG_test.pdf} &
% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b2jos_vetobtagwp70_highmet/BDTG_test.pdf} \\
% (b1) BDT discriminant in $t_h\tlhad$-2j & (b2) BDT discriminant in  $t_h\tlhad$-3j & (b3) BDT discriminant in $t_h\thadhad$-2j \\
% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b3jos_vetobtagwp70_highmet/BDTG_test.pdf} & \\
% (c1) BDT discriminant in$t_h\thadhad$-3j\\
% \end{tabular}
% \caption{ The BDT output distributions are compared between the expected background and $tqH$ signals in: $t_{\ell}\thadhad$ (a1),  $t_{\ell}\tauhad$-1j (a2),  $t_{\ell}\tauhad$-2j (a3),$t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (b3), and $t_h\thadhad$-3j (c1). Only statistical uncertainties are being shown (?). Underflow and overflow bins are included
% respectively in the first and last bins. Empty data bins here are always blinded based on our strategy. The real tau contributions shown from $t\bar{t}$ and other MC including % diboson, single top, and V+jets.}
% \label{fig:asimov_prefitbdt}
% \end{figure}
